```{r}
#install.packages("pacman")
library(pacman)

p_load(tidyverse, tidylog, purrr, tidymodels, tidytext, textrecipes, textclean, stringr, tokenizers, workflowsets, themis)

source("negex.R") #Load functions for negex to work
```

### 3 step process
1. Run negex to remove negated terms in text
2. Use regex to simplify some termes related to people who inject drugs
3. Use ML model to predict classification as PWID or NOT PWID

Need to have a dataframe with an ID for each text, and of course, the text. 
The dataframe should be called "df".
The IDs should be in a column "doc_id".
The text to be classified should be in a column "text". 
 
Below you can run the process individually, or go to the 5th chunk and run the code in one go.  

```{r Negex}
df <- data.frame(doc_id = c("1", "2", "3"),
                 text = c("57 y/o male report IVDU, heroin and methamphetamine use", 
                          "57 y/o male report IVDU, heroin and methamphetamine use",
                          "57 y/o female denies smoking, alcohol or injection drug use. Has been sober and on methadone for 12 years."))

#Annotate text using udpipe
annotated_text <- map(1:nrow(df), ~ {
  udpipe::udpipe_annotate(udmodel, x = df[.x,]$text, doc_id = df[.x, ]$doc_id,
                                          tokenizer = "tokenizer", tagger = "default",
                                          parser = "default") %>%
    as.data.frame(., detailed = TRUE)
}
)

#Use negex to tag negated toxens
negex.list <- map(annotated_text, ~{
  negex_processor(.x, negex_simp, 6)
}
)

#Remove negated tokens 
negex.remove <- map(negex.list, ~{
  .x %>% 
    filter(negated == FALSE) %>%
    filter(!negex_category %in% c("definiteNegatedExistence", "probableNegatedExistence")) %>%
    group_by(doc_id) %>% 
    summarise(text.neg = paste0(token, collapse = " ")) 
})

df.neg <- bind_rows(negex.remove)

df <- df %>% left_join(df.neg, by = "doc_id")
```

```{r Regex}
df <- df %>%
    mutate(text.neg = str_replace_all(text.neg, pattern = regex("intravenous drug use", ignore_case = T),  replacement = "IVDU")) %>%
  mutate(text.neg = str_replace_all(text.neg, pattern = regex("intravenous drug abuse", ignore_case = T), replacement = "IVDA")) %>%
  mutate(text.neg = str_replace_all(text.neg, pattern = regex("IV drug use", ignore_case = T), replacement = "IVDU")) %>%
  mutate(text.neg = str_replace_all(text.neg, pattern = regex("IV drug abuse", ignore_case = T), replacement = "IVDA")) %>%
  mutate(text.neg = str_replace_all(text.neg, pattern = regex("injection drug abuse", ignore_case = T), replacement = "IVDA")) %>%
  mutate(text.neg = str_replace_all(text.neg, pattern = regex("injection drug use", ignore_case = T), replacement = "IVDU"))

#write_rds(df, "Data/df_example.rds")  
```

```{r ML to predict}
#Import example data
df <- read_rds("Data/df_example.rds")

#Import model for prediction
test_fitted <- readRDS("Output/fit_model_predict.rds")

#Predict on new data
df.predicted <- bind_cols(df, 
          predict(test_fitted, new_data = df, type = "class"),
          predict(test_fitted, new_data = df, type = "prob"))
```

```{r All in one go}
df <- data.frame(doc_id = c("1", "2", "3"),
                 text = c("57 y/o male report IVDU, heroin and methamphetamine use", 
                          "57 y/o male report IVDU, heroin and methamphetamine use",
                          "57 y/o female denies smoking, alcohol or injection drug use. Has been sober and on methadone for 12 years."))

#Annotate text using udpipe
annotated_text <- map(1:nrow(df), ~ {
  udpipe::udpipe_annotate(udmodel, x = df[.x,]$text, doc_id = df[.x, ]$doc_id,
                                          tokenizer = "tokenizer", tagger = "default",
                                          parser = "default") %>%
    as.data.frame(., detailed = TRUE)
}
)

#Use negex to tag negated toxens
negex.list <- map(annotated_text, ~{
  negex_processor(.x, negex_simp, 6)
}
)

#Remove negated tokens 
negex.remove <- map(negex.list, ~{
  .x %>% 
    filter(negated == FALSE) %>%
    filter(!negex_category %in% c("definiteNegatedExistence", "probableNegatedExistence")) %>%
    group_by(doc_id) %>% 
    summarise(text.neg = paste0(token, collapse = " ")) 
})
df.neg <- bind_rows(negex.remove)

#Join back to original DF
df <- df %>% left_join(df.neg, by = "doc_id")

#Regex
df <- df %>%
    mutate(text.neg = str_replace_all(text.neg, pattern = regex("intravenous drug use", ignore_case = T),  replacement = "IVDU")) %>%
  mutate(text.neg = str_replace_all(text.neg, pattern = regex("intravenous drug abuse", ignore_case = T), replacement = "IVDA")) %>%
  mutate(text.neg = str_replace_all(text.neg, pattern = regex("IV drug use", ignore_case = T), replacement = "IVDU")) %>%
  mutate(text.neg = str_replace_all(text.neg, pattern = regex("IV drug abuse", ignore_case = T), replacement = "IVDA")) %>%
  mutate(text.neg = str_replace_all(text.neg, pattern = regex("injection drug abuse", ignore_case = T), replacement = "IVDA")) %>%
  mutate(text.neg = str_replace_all(text.neg, pattern = regex("injection drug use", ignore_case = T), replacement = "IVDU"))

#Import model for prediction
test_fitted <- readRDS("Output/fit_model_predict.rds")

#Predict on new data
df.predicted <- bind_cols(df, 
          predict(test_fitted, new_data = df, type = "class"),
          predict(test_fitted, new_data = df, type = "prob"))
```

```{r}
sessionInfo()
```
